---
title       : Predict Miles per Gallon of a Car
subtitle    : using Linear Model
author      : 
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Overview

- you know, how many horsepower you want in your car
- we can predict, how many miles per gallon such a car will have.
- to do that, we built a mathematical model and trained it on a real dataset

---

## Dataset

 - The data was extracted from the 1974 Motor Trend US magazine
 - see https://goo.gl/ZU7MTU for more details

```{r}
require(datasets)
head(mtcars)
```

---

## Model
- a linear model was build
- hourse power was used as a predictor for miles per galon
```{r}
fit<-lm(formula = mpg~hp, data = mtcars)
fit
```

---

## Visualisation
- The shiny application UI contains visualization of the linear model

```{r fig.height=3}
require(ggplot2)
qplot(hp, mpg, data = mtcars)+ xlab("Hourse power")+ylab("Miles per Gallon") +
                geom_abline(intercept = coef(fit)[1], slope=coef(fit)[2])
```
- checkout yourself: https://kbdata.shinyapps.io/shinyProject/
